target_offtarget

### 2025-04-13 manuscript_figures.Rmd
Update figure S8

FLU_ME2 <- persite_norm |>
  filter(virus == "Influenza_B_virus") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p2") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("Coverage") +
  ggtitle("Influenza B virus (Background M2 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols4, label = c(expression("10"^"2"), expression("10"^"3"), expression("10"^"5")))

>>>>

FLU_ME2 <- persite_norm |>
  filter(virus == "Influenza_B_virus") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p8") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("Coverage") +
  ggtitle("Influenza B virus (Background M2 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols4, label = c(expression("10"^"2"), expression("10"^"3"), expression("10"^"5")))
